The importance of measurement uncertainty in ecological management

### 2018-01-30 manuscripts/manuscript.Rmd

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7,  dev="cairo_pdf", cache = TRUE)
library(tidyverse)
library(gridExtra)
```

```{r optional_plot_fonts, message=FALSE}
library(ggplot2)
library(Cairo)
library(extrafont)
library(hrbrthemes)
extrafont::loadfonts()
knitr::opts_chunk$set()
#hrbrthemes::import_roboto_condensed() 
#ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
ggplot2::theme_set(hrbrthemes::theme_ipsum())
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", 
             "#FDB515", "#00B0DA",  "#CFDD45")
colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: high prior",
                      "biomass",
                      "catch"))
scale_colour_discrete <- function(...) scale_colour_manual(..., values=colors)
scale_fill_discrete <- function(...) scale_fill_manual(..., values=colors)
```

>>>>

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(tidyverse)
library(gridExtra)
```

```{r optional_plot_fonts, message=FALSE}
library(ggplot2)
#library(Cairo)
library(extrafont)
library(hrbrthemes)
extrafont::loadfonts()
knitr::opts_chunk$set()
#hrbrthemes::import_roboto_condensed() 
#ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
ggplot2::theme_set(hrbrthemes::theme_ipsum())
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", 
             "#FDB515", "#00B0DA",  "#CFDD45")
colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: high prior",
                      "biomass",
                      "catch"))
scale_colour_discrete <- function(...) scale_colour_manual(..., values=colors)
scale_fill_discrete <- function(...) scale_fill_manual(..., values=colors)
```
